---
title: "Spansion LLC + DVISD<br>"
subtitle: "Amendment to Existing 313 Agreement"
date: "today"
date-format: long
author: "Matt Worthington"
format:
  revealjs: 
    include-in-header: header.html 
    theme: [default, custom.scss]
editor: visual
---

## Recapping Existing Agreement

<hr>
<br>

Among other things, the application approved between Del Valle + Spansion LLC on August agreed to the following[^1]:

[^1]: [August 16, 2022 Meeting Minutes](https://meetings.boardbook.org/Documents/CustomMinutesForMeeting/675?meeting=541240)

-   It capped Spansion LLC's M+O Taxable Values at \$80 million dollars[^2].
-   Guaranteed 40 "qualifying" jobs and 60 qualifying jobs.[^3]
-   It effectively reduces your tax liability between now and 2038 by an estimate $8.9 million dollars[^4].

[^2]: [See Page 176 of August 16th, 2022 Meeting Agenda](https://meetings.boardbook.org/Documents/CustomAgendaForMeeting/675?meeting=541240)

[^3]: [See Page 174 of August 16th, 2022 Meeting Agenda](https://meetings.boardbook.org/Documents/CustomAgendaForMeeting/675?meeting=541240)

[^4]: [See Attachment A of Certification Packet on Texas Comptroller Site](https://assets.comptroller.texas.gov/ch313/1696/1696-del-spansion-cert.pdf)

# Value Limitation

## Example Scenario: Before Agreement

<hr>
<br>

Suppose you planned to build a facility that would end up being appraised for $120 million dollars. 

```{r}
#| echo: false
library(tidyverse)
library(hrbrthemes)
library(ggiraph)

ex_1 <- tibble(
  value_lbl = c("Limited Value", "Actual Value"),
  value = c(80000000, 120000000)
)

ex_gg <- ex_1 |> 
  filter(value_lbl == "Actual Value") |> 
  ggplot() +
  aes(y = "Value",  x = value) +
  geom_col(alpha = 0.3) +
  geom_text(aes(y = "Value", x = 60000000), 
            label = "Actual Value",
            family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'",
            fontface = "bold",
            color = "#2d2d2d") +
  theme_ipsum(base_family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'") +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank()) +
  labs(x = NULL,
       y = NULL) +
  scale_x_comma(labels = scales::dollar_format(scale=0.000001, suffix = "M"))

ggiraph(ggobj = ex_gg,
        width = 1,
        height_svg = 2.5)
```

## Example Scenario: After Agreement

<hr>
<br>

My understanding is that the agreement you executed with Del Valle ISD on August 16th would [reduce your taxable value by $40 million]{style="background-color: #c2f0c2;"}.

```{r}
#| echo: false
library(tidyverse)
library(hrbrthemes)
library(ggiraph)

ex_1 <- tibble(
  value_lbl = c("Limited Value", "Actual Value"),
  value = c(80000000, 120000000)
)

ex_gg <- ex_1 |> 
  filter(value_lbl == "Actual Value") |> 
  ggplot() +
  aes(y = "Value",  x = value) +
  geom_col(fill = "#29a329",
           alpha = 0.4) +
  geom_col(data = ex_1 |> filter(value_lbl == "Limited Value"),
           aes(y = "Value",  x = value),
           fill = "#2d2d2d",
           alpha = 0.7) +
  geom_text(aes(y = "Value", x = 40000000), 
            label = "Limited Value ($80M)",
            fontface = "bold",
            family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'",
            color = "white") +
  geom_text(aes(y = "Value", x = 100000000), 
            label = "Savings ($40M)",
            fontface = "bold",
            family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'",
            color = "black") +
  theme_ipsum(base_family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'") +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank()) +
  labs(x = NULL,
       y = NULL) +
  scale_x_comma(labels = scales::dollar_format(scale=0.000001, suffix = "M"))

ggiraph(ggobj = ex_gg,
        width = 1,
        height_svg = 2.5)
```

## Impact on M+O: Existing Agreement  
<hr>

The net impact of the \$80 Million cap is an estimated [\$1 Billion reduction]{style="background-color: #c2f0c2;"} in Spansion's taxable M+O value over a 9-year period. 

```{r}
#| echo: false
#| eval: false
library(googlesheets4)
library(tidyverse)
library(hrbrthemes)
library(ggiraph)

url <- "https://docs.google.com/spreadsheets/d/1CgRJnjalxVkjVbZsdtK6b9rkoHS7I_o-fYgx3GZAe-o/edit#gid=1591780990"

wo_impact <- read_sheet(url, sheet = "Without Incentives") |> 
  janitor::clean_names() |> 
  filter(!is.na(year)) |> 
  select(-x4) |> 
  pivot_longer(cols = estimated_taxable_value_for_i_s:estimated_total_property_taxes,
               values_to = "wo_limits") |> glimpse()

with_impact <- read_sheet(url, sheet = "With Incentives") |> 
  janitor::clean_names() |> 
  filter(!is.na(year)) |> 
  select(-x4) |> 
  pivot_longer(cols = estimated_taxable_value_for_i_s:estimated_total_property_taxes,
               values_to = "with_limits") |> glimpse()

act_impact <- wo_impact |> 
  left_join(with_impact, by = c("year", "name")) |> 
  mutate(impact = wo_limits - with_limits)

arrow::write_parquet(act_impact, "spansion_delvalle_limitation_data.parquet")
```

```{r}
act_impact <- arrow::read_parquet("spansion_delvalle_limitation_data.parquet") |>
  filter(name == "estimated_taxable_value_for_m_o") |> 
  mutate(wo_lbl = scales::dollar(wo_limits, scale=0.000001, accuracy = 0.01, suffix = "M"),
         impact_lbl = if_else(impact < 1000000,
                              scales::dollar(impact, scale=0.001, accuracy = 1, suffix = "K"),
                              scales::dollar(impact, scale=0.000001, accuracy = 1, suffix = "M")))

act_gg <- act_impact |> 
  ggplot() +
  aes(y = with_limits,  x = year) +
  geom_col_interactive(data = act_impact,
           aes(y = wo_limits,  x = year), 
           fill = "#29a329",
           alpha = 0.4) +
    geom_col_interactive(alpha = 0.7,
           fill = "#2d2d2d") +
    geom_hline(yintercept = 80000000,
               color = "black",
               linetype = 2) +
    geom_text_interactive(data = act_impact |> filter(impact!=0),
            aes(y = wo_limits, label = impact_lbl, x = year),
            fontface = "bold",
            vjust = -0.5,
            size = 2.15,
            family = "Ringside Narrow SSm A",
            color = "#1f7a1f") +
  geom_curve(data = data.frame(x = 2034.54524826865, y = 174950345.902679, xend = 2033.73411856584, yend = 84977557.721121),
             mapping = aes(x = x, y = y, xend = xend, yend = yend),
             curvature = 0.1, arrow = arrow(30L, unit(0.1, "inches"),
                                            "last", "closed"),
             inherit.aes = FALSE) + 
  geom_label(data = data.frame(x = 2035.41646165315, y = 173627216.664715, label = "$80 Million M+O Cap "),
             mapping = aes(x = x, y = y, label = label),
             label.padding = unit(0.25, "lines"),
             label.r = unit(0.25, "lines"),
             size = 2.5,
             family = "Ringside Narrow SSm A",
             inherit.aes = FALSE) +
  theme_ipsum() +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.text.x = element_text(size = 7, family = "Ringside Narrow SSm A"),
        axis.text.y = element_text(size = 7, family = "Ringside Narrow SSm A")) +
  labs(x = NULL,
       y = NULL) +
  scale_x_continuous(breaks = c(2024, 2026, 2028, 2030, 2032, 2034, 2036, 2038)) +
  scale_y_comma(labels = scales::dollar_format(scale=0.000001, accuracy = 1, suffix = "M"),
                limits = c(0, 400000000))

ggiraph(ggobj = act_gg,
        width = 1,
        height_svg = 3)
```

## Impact on Tax Liability: Existing Agreement
<hr>

The net impact of the value limitation is an estimated [$8.9 million reduction]{style="background-color: #c2f0c2;"} in Spansion's tax liabililty over a 9-year period. 

```{r}
act_impact <- arrow::read_parquet("spansion_delvalle_limitation_data.parquet") |>
  filter(name == "del_valle_isdm_o_tax_levy") |> 
  mutate(wo_lbl = scales::dollar(wo_limits, scale=0.000001, accuracy = 0.01, suffix = "M"),
         impact_lbl = if_else(impact < 1000000,
                              scales::dollar(impact, scale=0.001, accuracy = 1, suffix = "K"),
                              scales::dollar(impact, scale=0.000001, accuracy = 0.1, suffix = "M")))

act_gg <- act_impact |> 
  ggplot() +
  aes(y = with_limits,  x = year) +
  geom_hline(yintercept = 697600,
             color = "black",
             linetype = 2) +
  geom_col_interactive(data = act_impact,
                       aes(y = wo_limits,  x = year), 
                       fill = "#29a329",
                       alpha = 0.4) +
  geom_col_interactive(alpha = 0.7,
                       fill = "#2d2d2d") +
  geom_text_interactive(data = act_impact |> filter(impact!=0),
                        aes(y = wo_limits, label = impact_lbl, x = year),
                        fontface = "bold",
                        vjust = -0.5,
                        size = 2.25,
                        family = "Ringside Narrow SSm A",
                        color = "#1f7a1f") +
  geom_curve(data = data.frame(x = 2029.50208185774, y = 2399119.08906237, xend = 2026.1215759008, yend = 1785517.90495652),
             mapping = aes(x = x, y = y, xend = xend, yend = yend),
             angle = 85L, curvature = 0.4, arrow = arrow(30L, unit(0.1, "inches"),
                                                         "last", "closed"),
             inherit.aes = FALSE) + 
  ggtext::geom_richtext(data = data.frame(x = 2029.56032720078, y = 2487541.70823018, label = "<span style = 'color:#2eb82e;'>Savings</span>"),
                        mapping = aes(x = x, y = y, label = label),
                        size = 2.5,
                        family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'",
                        label.padding = unit(0.25, "lines"),
                        label.r = unit(0.15, "lines"),
                        inherit.aes = FALSE) +
  theme_ipsum(base_family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'") +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.text.x = element_text(size = 7, family = "Ringside Narrow SSm A"),
        axis.text.y = element_text(size = 7, family = "Ringside Narrow SSm A")) +
  labs(x = NULL,
       y = NULL) +
  scale_x_continuous(breaks = c(2024, 2026, 2028, 2030, 2032, 2034, 2036, 2038)) +
  scale_y_comma(labels = scales::dollar_format(scale=0.000001, accuracy = 1, suffix = "M"),
                limits = c(0, 3500000))

ggiraph(ggobj = act_gg,
        width = 1,
        height_svg = 3)
```

# Supplemental Payments

## Example Scenario: $40M Savings

<hr>

```{r}
#| echo: false
library(tidyverse)
library(hrbrthemes)
library(ggiraph)

ex_1 <- tibble(
  value_lbl = c("Limited Value", "Actual Value"),
  value = c(80000000, 120000000)
)

ex_gg <- ex_1 |> 
  filter(value_lbl == "Actual Value") |> 
  ggplot() +
  aes(y = "Value",  x = value) +
  geom_col(alpha = 0.8) +
  geom_col(data = ex_1 |> filter(value_lbl == "Limited Value"),
           aes(y = "Value",  x = value),
           fill = "red",
           alpha = 0.8) +
  geom_text(aes(y = "Value", x = 40000000), 
            label = "Limited Value ($80M)",
            fontface = "bold",
            family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'",
            color = "white") +
  geom_text(aes(y = "Value", x = 100000000), 
            label = "Savings ($40M)",
            family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'",
            fontface = "bold",
            color = "white") +
  theme_ipsum(base_family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'") +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank()) +
  labs(x = NULL,
       y = NULL) +
  scale_x_comma(labels = scales::dollar_format(scale=0.000001, suffix = "M"))

ggiraph(ggobj = ex_gg,
        width = 1,
        height_svg = 1.75)
```

In any scenario, Spansion LLC would pay DVISD $100 per student for any savings in excess of the limitation. Is that correct? For example..

$$ \$100_\text{Per Student}*9,675.142_\text{ADA} = \color{red}{\textbf{\$965.5k}}$$

# Jobs Benefit in Del Valle

## Qualifying Jobs

“Qualifying job” means a permanent, full-time job that:

* requires at least 1,600 hours of work a year;
* is not transferred from one area in this state to another area in this state;
* is not created to replace a previous employee;
* is covered by a group health benefit plan for which the business offers to pay at least 80 percent of the premiums or other charges assessed for employee-only coverage under the plan, regardless of whether an employee may voluntarily waive the coverage; and
* pays at least 110 percent of the county average weekly wage for manufacturing jobs in the county where the job is located.

## Original Spansion Agreement: 100 Jobs

<hr>

In the original agreement, Spansion LLC agreed to provide 100 jobs. 40 were qualifying. 60 were non-qualifying. In Del Valle, qualifying annual wages would be \$68,558.60 for a [total annual qualifying jobs guarantee valued at \$2,742,344]{style="background-color: #c2f0c2;"} during the period of agreement.

```{r}
#| echo: false
library(tidyverse)
library(hrbrthemes)
library(ggiraph)

ex_1 <- tibble(
  value_lbl = c("Qualifying", "Non-Qualifying"),
  value = c(40, 60)
)

ex_gg <- ex_1 |> 
  filter(value_lbl == "Qualifying") |>
  ggplot() +
  aes(y = "Value",  x = value) +
  geom_col(alpha = 0.6,
           fill = "blue") +
  geom_col(aes(y = "Value",  x = 100),
           fill = "darkblue",
           alpha = 0.6) +
  geom_text(aes(y = "Value", x = 20), 
            label = "Qualifying",
            family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'",
            fontface = "bold",
            color = "white") +
  geom_text(aes(y = "Value", x = 70), 
            label = "Non-Qualifying",
            family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'",
            fontface = "bold",
            color = "white") +
  theme_ipsum(base_family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'") +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank()) +
  labs(x = NULL,
       y = NULL) +
  scale_x_comma(labels = scales::number_format(scale=1, suffix = " Jobs"))

ggiraph(ggobj = ex_gg,
        width = 1,
        height_svg = 2.25)
```

## Current Amendment's Impact

<hr>

In the current proposal, Spansion LLC is asking to eliminate 15 qualifying jobs and all 60 non-qualifying jobs. The elimination of [the 15 qualifying jobs reduction would be roughly $1 million each year in lost guaranteed wages]{style="background-color: #ffcccc;"} to our community in Del Valle. 

```{r}
#| echo: false
library(tidyverse)
library(hrbrthemes)
library(ggiraph)

ex_1 <- tibble(
  value_lbl = c("Qualifying", "Non-Qualifying"),
  value = c(40, 60)
)

ex_gg <- ex_1 |> 
  filter(value_lbl == "Qualifying") |>
  ggplot() +
  aes(y = "Value",  x = value) +
  geom_col(aes(y = "Value",  x = 25),
           alpha = 0.6,
           fill = "blue") +
  geom_col(aes(y = "Value",  x = 100),
           fill = "darkblue",
           # color = "blue",
           alpha = 0) +
  geom_text(aes(y = "Value", x = 12.5), 
            label = "25 Qualifying",
            family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'",
            fontface = "bold",
            color = "white") +
  geom_text(aes(y = "Value", x = 56.25), 
            label = "75 Total Jobs Eliminated",
            fontface = "bold",
            family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'",
            color = "black") +
  annotate(geom = "rect", alpha = 0, color = "#6d6d6d", linetype = 2,
           xmin = 25, xmax = 100, ymin = .55, ymax = 1.45) +
  theme_ipsum(base_family = "'Ringside Narrow SSm A', 'Ringside Narrow SSm B'") +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank()) +
  labs(x = NULL,
       y = NULL) +
  scale_x_comma(labels = scales::number_format(scale=1, suffix = " Jobs"))

ggiraph(ggobj = ex_gg,
        width = 1,
        height_svg = 2.25)
```
