---
title: "Spansion LLC + DVISD<br>"
subtitle: "Amendment to Existing 313 Agreement"
date: "today"
date-format: long
author: "Matt Worthington"
format:
  revealjs: 
    include-in-header: header.html 
    theme: [default, custom.scss]
editor: visual
---

## Recapping Existing Agreement

<hr>
<br>

Among other things, the application approved between Del Valle + Spansion LLC on August agreed to the following[^1]:

[^1]: [August 16, 2022 Meeting Minutes](https://meetings.boardbook.org/Documents/CustomMinutesForMeeting/675?meeting=541240)

-   It capped Spansion LLC's M+O Taxable Values at \$80 million dollars[^2].
-   Guaranteed 40 "qualifying" jobs and 60 qualifying jobs.[^3]

[^2]: [See Page 176 of August 16th, 2022 Meeting Agenda](https://meetings.boardbook.org/Documents/CustomAgendaForMeeting/675?meeting=541240)

[^3]: [See Page 174 of August 16th, 2022 Meeting Agenda](https://meetings.boardbook.org/Documents/CustomAgendaForMeeting/675?meeting=541240)

# Value Limitation

## Example Scenario: Before Agreement

<hr>
<br>

Suppose you planned to build a facility that would end up being appraised for $120 million dollars. 

```{r}
#| echo: false
library(tidyverse)
library(hrbrthemes)
library(ggiraph)

ex_1 <- tibble(
  value_lbl = c("Limited Value", "Actual Value"),
  value = c(80000000, 120000000)
)

ex_gg <- ex_1 |> 
  filter(value_lbl == "Actual Value") |> 
  ggplot() +
  aes(y = "Value",  x = value) +
  geom_col(alpha = 0.8) +
  geom_text(aes(y = "Value", x = 60000000), 
            label = "Actual Value",
            fontface = "bold",
            color = "white") +
  theme_ipsum() +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank()) +
  labs(x = NULL,
       y = NULL) +
  scale_x_comma(labels = scales::dollar_format(scale=0.000001, suffix = "M"))

ggiraph(ggobj = ex_gg,
        width = 1,
        height_svg = 2.5)
```

## Example Scenario: After Agreement

<hr>
<br>

My understanding is that the agreement you executed with Del Valle ISD on August 16th would reduce your taxable value by $40 million.
```{r}
#| echo: false
library(tidyverse)
library(hrbrthemes)
library(ggiraph)

ex_1 <- tibble(
  value_lbl = c("Limited Value", "Actual Value"),
  value = c(80000000, 120000000)
)

ex_gg <- ex_1 |> 
  filter(value_lbl == "Actual Value") |> 
  ggplot() +
  aes(y = "Value",  x = value) +
  geom_col(alpha = 0.8) +
  geom_col(data = ex_1 |> filter(value_lbl == "Limited Value"),
           aes(y = "Value",  x = value),
           fill = "red",
           alpha = 0.8) +
  geom_text(aes(y = "Value", x = 40000000), 
            label = "Limited Value ($80M)",
            fontface = "bold",
            color = "white") +
  geom_text(aes(y = "Value", x = 100000000), 
            label = "Savings ($40M)",
            fontface = "bold",
            color = "white") +
  theme_ipsum() +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank()) +
  labs(x = NULL,
       y = NULL) +
  scale_x_comma(labels = scales::dollar_format(scale=0.000001, suffix = "M"))

ggiraph(ggobj = ex_gg,
        width = 1,
        height_svg = 2.5)
```

# Supplemental Payments

## Example Scenario: $40M Savings

<hr>

```{r}
#| echo: false
library(tidyverse)
library(hrbrthemes)
library(ggiraph)

ex_1 <- tibble(
  value_lbl = c("Limited Value", "Actual Value"),
  value = c(80000000, 120000000)
)

ex_gg <- ex_1 |> 
  filter(value_lbl == "Actual Value") |> 
  ggplot() +
  aes(y = "Value",  x = value) +
  geom_col(alpha = 0.8) +
  geom_col(data = ex_1 |> filter(value_lbl == "Limited Value"),
           aes(y = "Value",  x = value),
           fill = "red",
           alpha = 0.8) +
  geom_text(aes(y = "Value", x = 40000000), 
            label = "Limited Value ($80M)",
            fontface = "bold",
            color = "white") +
  geom_text(aes(y = "Value", x = 100000000), 
            label = "Savings ($40M)",
            fontface = "bold",
            color = "white") +
  theme_ipsum() +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank()) +
  labs(x = NULL,
       y = NULL) +
  scale_x_comma(labels = scales::dollar_format(scale=0.000001, suffix = "M"))

ggiraph(ggobj = ex_gg,
        width = 1,
        height_svg = 1.75)
```

And, in any scenario, Spansion LLC would pay DVISD $100 per student for any savings in excess of the limitation. Is that correct? For example..

$$ \$100_\text{Per Student}*\text{11,000 Students} = \color{red}{\textbf{\$1.1 Million}}$$

# Jobs Benefit in Del Valle

## Qualifying Jobs

“Qualifying job” means a permanent, full-time job that:

* requires at least 1,600 hours of work a year;
* is not transferred from one area in this state to another area in this state;
* is not created to replace a previous employee;
* is covered by a group health benefit plan for which the business offers to pay at least 80 percent of the premiums or other charges assessed for employee-only coverage under the plan, regardless of whether an employee may voluntarily waive the coverage; and
* pays at least 110 percent of the county average weekly wage for manufacturing jobs in the county where the job is located.

## Original Spansion Agreement: 100 Jobs

<hr>

In the original agreement, Spansion LLC agreed to provide 100 jobs. 40 were qualifying. 60 were non-qualifying. In Del Valle, qualifying wage would be \$68,558.60 for a total qualifying jobs guarantee of \$2,742,344 during period of agreement.

```{r}
#| echo: false
library(tidyverse)
library(hrbrthemes)
library(ggiraph)

ex_1 <- tibble(
  value_lbl = c("Qualifying", "Non-Qualifying"),
  value = c(40, 60)
)

ex_gg <- ex_1 |> 
  filter(value_lbl == "Qualifying") |>
  ggplot() +
  aes(y = "Value",  x = value) +
  geom_col(alpha = 0.6,
           fill = "blue") +
  geom_col(aes(y = "Value",  x = 100),
           fill = "darkblue",
           alpha = 0.6) +
  geom_text(aes(y = "Value", x = 20), 
            label = "Qualifying",
            fontface = "bold",
            color = "white") +
  geom_text(aes(y = "Value", x = 70), 
            label = "Non-Qualifying",
            fontface = "bold",
            color = "white") +
  theme_ipsum() +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank()) +
  labs(x = NULL,
       y = NULL) +
  scale_x_comma(labels = scales::number_format(scale=1, suffix = " Jobs"))

ggiraph(ggobj = ex_gg,
        width = 1,
        height_svg = 2.25)
```

## Current Amendment's Impact

<hr>

In the current proposal, Spansion LLC is asking to eliminate 15 qualifying jobs and all 60 non-qualifying jobs. Is that right?

```{r}
#| echo: false
library(tidyverse)
library(hrbrthemes)
library(ggiraph)

ex_1 <- tibble(
  value_lbl = c("Qualifying", "Non-Qualifying"),
  value = c(40, 60)
)

ex_gg <- ex_1 |> 
  filter(value_lbl == "Qualifying") |>
  ggplot() +
  aes(y = "Value",  x = value) +
  geom_col(aes(y = "Value",  x = 25),
           alpha = 0.6,
           fill = "blue") +
  geom_col(aes(y = "Value",  x = 100),
           fill = "darkblue",
           # color = "blue",
           alpha = 0) +
  geom_text(aes(y = "Value", x = 12.5), 
            label = "25 Qualifying",
            fontface = "bold",
            color = "white") +
  geom_text(aes(y = "Value", x = 56.25), 
            label = "75 Total Jobs Eliminated",
            fontface = "bold",
            color = "black") +
  annotate(geom = "rect", alpha = 0, color = "#6d6d6d", linetype = 2,
           xmin = 25, xmax = 100, ymin = .55, ymax = 1.45) +
  theme_ipsum() +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank()) +
  labs(x = NULL,
       y = NULL) +
  scale_x_comma(labels = scales::number_format(scale=1, suffix = " Jobs"))

ggiraph(ggobj = ex_gg,
        width = 1,
        height_svg = 2.25)
```
